%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Mail Carrier (Seasonal)} % Job title
    {La Poste} % Organization
    {France} % Location
    {Various Periods, Jul. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engaged in seasonal employment as a mail carrier, including periods in Jul. 2016, Jul.-Aug. 2017, and Apr. 2018.}
        \item {Provided reliable mail and package delivery services during high-demand periods, ensuring timely distribution.}
        \item {Adapted to various routes and postal responsibilities, showcasing flexibility and quick learning abilities.}
        \item {Demonstrated organizational and time-management skills to efficiently handle high-volume mail sorting and delivery tasks.}
        \item {Maintained professional customer interactions, effectively addressing inquiries and offering service information.}
        \item {Collaborated with team members to manage workloads and ensure comprehensive delivery area coverage.}
        \item {Displayed physical endurance in managing extensive daily routes and adapting to different weather conditions.}
      \end{cvitems}
    }

  \cventry
    {Fusilier Marin} % Job title
    {Marine Nationale} % Organization
    {France} % Location
    {Oct. 2018 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed strong team collaboration and leadership skills in high-pressure and demanding military environments.}
        \item {Managed and led diverse teams, demonstrating effective communication, decision-making, and problem-solving abilities.}
        \item {Applied rigorous discipline and strategic planning skills to complex situations, ensuring successful mission outcomes.}
        \item {Trained extensively in various physical and tactical skills, enhancing personal resilience and adaptability.}
        \item {Gained valuable experience in working in multinational teams, fostering a broad understanding of different cultures and working styles.}
        \item {Leveraged technology in various aspects of military operations, bridging my military experience with my advanced studies in technology at 42 Le Havre.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
